S-process Enhancement in Barium Disk Stars

### 2018-01-19 article/ms.tex
Put Out Work Evening Riter

\begin{abstract}
In this paper we present the analysis of 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements. Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses. Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star. Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model. We determined ...

@@

In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements. Specifcally, the giants studied here display especially molecular band absorption for CH, CN, and C$_2$ molecular bands, and strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. In Section \ref{sec:obs} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign in Section \ref{sec:an}. In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}

\section{Observations and Target Selection} \label{sec:obs}
The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}\countertodo{I read it in a paper somewhere, is it not true ?}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.

The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. A negative residual as shown in the poster child figure \ref{fig:figure1} illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. We used five filters that each spectra for both enhancement lines had to meet to be considered a Barium star candidate, these included:

@@

\section{Analysis and Results}  \label{sec:an}
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{HRdummy.png}
    \caption{HR Diagram}
    \label{fig:figure2}
\end{figure}

@@

\subsection{Line Selection and Atmospheric Parameters}

\subsection{Technetium Lines}

\subsection{Abundance Analysis}
\subsection{Abundance Uncertainties}

@@

\subsection{HR Diagram}

\subsection{Abundances}
\subsubsection{Rejected Stars}
\subsubsection{Sodium Abundance}
\subsubsection{Heavy Element Abundance}
\subsection{Kinematics}

@@

I thank Andrew R. Casey for finally re-hiring me.

@@

Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W. Rix, H.-W. Liu, C. Yang, F. Zhang, Y. Hou,\& Y. Wang, Y. 2017, 

@@

\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{(2015)}]{luo2015}

@@

>>>>

\begin{abstract}
In this paper we present the analysis of 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements. Barium stars exist as either intrinsic TP-AGB stars, producing enhancements in s-process elements via cyclic thermal pulses. Or, extrinsic giants still on the main sequence with enhancements in s-process element the results of polluton from a binary TP-AGB star. Enhancements in \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements through a data-driven analysis given a well-fitted model. We determined ... Sodium enrichment was present in 5 of our barium star candidates and could be attributed to the NeNa cycle in more evolved stars.

@@

In this paper we analysis 454,180 giant stars from LAMOST data release (DR) 2 to identify and examine 257 Barium star candidates that show enhancements of s-process elements. Specifcally, the giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. Additionally, molecular band absorption for G Band, CH bands is observed. In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis follow up our follow-up observing campaign with MAGGELLAN. In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}

\section{Methods} \label{sec:methods}
\subsection{LAMOST Analysis}
\subsubsection{Data-driven Analysis}
The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}\countertodo{I read it in a paper somewhere, is it not true ?}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.

\subsubsection{Candidate Selection} \label{sec:cand}
The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. A negative residual as shown in the poster child figure \ref{fig:figure1} illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. We used five filters that each spectra, for both enhancement lines, had to meet to be considered a Barium star candidate; these included:

@@

\subsubsection{Technetium Lines}

Enhancement of technetium lines in our sample would indicate the presence of high luminosity Tc-self-enriched AGB S stars \citep{jorissen1993} and, suggest our candidates are infact intrinsic Barium stars. We undertook an identical analysis to the process described in Section \ref{sec:cand}, negative residuals for Tc enhancement lines 4049\AA, 4238.19\AA, 4262.27\AA, 4297\AA, and 5924.47\AA\hspace{0.2mm} were filtered for. In agreement with previous findings \citep[e.g.][]{little1987,smith1984,smith1983}, the results indicate that none of the evolved barium stars in our sample exhibited the presence of Tc enhancement. It is noted, \todo{51} of our barium candidates were enhanced in Tc lines, although, this is attributed to \todo{something} and is disregarded.

\subsubsection{Carbon Bands}

\subsubsection{Sodium Doublet}

According to \citet{el1995}, sodium overabundance observed in the atmospheres of A-F supergiant stars is synthesized in the convective core of main-sequence stars in the NeNa reaction chain. Sodium is transported to the surface of these supergiants via mixing of CNO cycle products during the first dredge-up, this constrains sodium enhancement to supergiants and giants only. \citet{antipova2004} discovered a sodium enhancement in a number of their barium star candidates, they relate this to the dredge-up of nuclear-burning material produced by convection during the red-giant phase. Moreover, they suggest [Na/Fe] values do not exhibit variations in metallicity, but [Na/Fe] ratios exhibit systematically higher values for giants with lower log g values. Similarily, \citet{decastro2016} highlights the possible weak, but statistically significant anti-correlation between [Na/Fe] ratio and log g, and illustrates this trend in previous studies\citep[e.g.][]{boyarchuk2002,mishenina2006,luck2007,takeda2008}.

Through an identical analysis to the process described in Section \ref{sec:cand}, we filtered for negative residuals in the enhanced sodium doublet lines 5889.950\AA\hspace{0.2mm} and 5895.924\AA. Our analysis produced 5 matches with our barium star candidates, this suggests sodium-rich material from the TP-AGB star polluted the barium star. Although, it's important to note a star with a minimum 1.5$M_\odot$ can exhibit sodium abundance through the NeNc cycle \citep{denissenkov1987}. During the giant phase synthesized sodium is brought to the surface via the first dredge-up, therefore, these candidates may display sodium enhancement without mass transfer from a TP-AGB star.

\subsection{MAGELLAN Analysis}

\subsubsection{Observations}

\subsubsection{Abundance Analysis}

\subsubsection{Abundance Uncertainties}

\subsection{Dynamics}
The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, producing 21 matches, and then using gala Python package to intergrate the galactic dynamics. The Milky Way potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.

@@

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{energy_angmomz.png}
    \caption{Energy Vs. Angular Momentum in Z}
    \label{fig:figure3}
\end{figure}

@@

\subsection{HR Diagram}
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{HRdummy.png}
    \caption{HR Diagram}
    \label{fig:figure2}
\end{figure}

@@

To John Power, hold in there buddy

@@

Ho, A.~Y.~Q., Ness, M.~K., Hogg, D.~W., Rix, H.-W. Liu, C., Yang, F., Zhang, Y., Hou, Y.,\& Wang, Y. 2017, 

@@

\bibitem[\protect\citeauthoryear{Luo A.L., Bai Z.R. et al}{2015}]{luo2015}

@@

\bibitem[\protect\citeauthoryear{Jorissen et al.}{1993}]{jorissen1993}
Jorissen, A., Frayer, D.~T., Johnson, H.~W., Mayor, M.,\& Smith, V.~V. 1993, 
A$\&$A, 271, 463
\bibitem[\protect\citeauthoryear{Little-Marenin \& Little}{1987}]{little1987}
Little-Marenin, I.~R.,\& Little, S.~J. 1987, 
AJ, 93, 1539
\bibitem[\protect\citeauthoryear{Smith}{1984}]{smith1984}
Smith, V.~V. 1984, 
A$\&$A, 132, 326
\bibitem[\protect\citeauthoryear{Smith \& Wallerstein}{1983}]{smith1983}
Smith, V.~V.,\& Wallerstein, G. 1983, 
ApJ, 273, 742
\bibitem[\protect\citeauthoryear{El Eid \& Champagne}{1995}]{el1995}
El Eid, M.~F.,\& Champagne, A.~E. 1995, 
ApJ, 451, 298
\bibitem[\protect\citeauthoryear{Antipova et al.}{2004}]{antipova2004}
Antipova, L.~I., Boyarchuk, A.~A., Pakhomov, Yu.~V.,\& Panchuk, V.~E. 2004, 
ARep, 48, 597
\bibitem[\protect\citeauthoryear{Boyarchuk et al.}{2002}]{boyarchuk2002}
Boyarchuk, A.~A., Pakhomov, Y.~V., Antipova, L.~I.,\& Boyarchuk, M.~E. 2002, 
ARep, 46, 819
\bibitem[\protect\citeauthoryear{Takeda et al.}{2008}]{takeda2008}
Takeda, Y., Sato, B.~V.,\& Murata, D. 2008, 
AJ, 60, 781
\bibitem[\protect\citeauthoryear{Mishenina et al.}{2006}]{mishenina2006}
Mishenina, T.~V., Bienaym\' e, O., Gorbaneva, T.~I.,\& Charbonnel, C. 2006, 
A$\&$A, 456, 1109
\bibitem[\protect\citeauthoryear{Luck \& Heiter}{2007}]{luck2007}
Luck R.~E.,\& Heiter, U. 2007, 
AJ, 133, 2464
\bibitem[\protect\citeauthoryear{Denissenkov \& Ivanov}{1987}]{denissenkov1987}
Denissenkov P.~A.,\& Ivanov, V.~V. 1987, 
SvAL, 13, 214
\bibitem[\protect\citeauthoryear{de Castro et al.}{2016}]{decastro2016}
de Castro, D.~B., Pereira, C.~B., Roig, F., Jilinski, E., Drake, N.~A., Chavero, C.,\& Sales Silva, J.~V. 2016, 
MNRAS, 459, 4299
